---
title: "Lab Assignment 3"
author: "Dylan Berneman"
date: '2023-04-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Question 1
Consider the AR(2) process below:
$$
\begin{aligned}
X_t = 0.8\ X_{t-1}\ - 0.12\ X_{t-2}\ + Z_{t}\ \text{with }Z_{t}  \stackrel{iid}{\sim} N(0, 1)
\end{aligned}
$$
\setlength{\leftskip}{2cm}

  (a) Express the process in terms of the back shift operator, *B*.  
  
  $$Z_{t}=(1-0.8\ B+0.12\ B^2)X_{t}$$
  
  (b) Determine whether each process is causal and/or invertible. (Hint: use *polyroot()*)\
```{r}
polyroot(c(1,-0.8,0.12))
```
  Since the roots are outside of the unit circle, the AR(2) model is causal.
  
  (c) Plot the sample ACF and PACF after simulating 200 observations from this AR(2) model with the following code:  
```{r}
set.seed(1234)
ar2 <- arima.sim(model = list(ar = c(0.8, -0.12), sd = 1), n = 200)
acf(ar2)
```  
  (d) Use the above simulation to **manually** construct the Yule-Waker estimate $\hat{\phi}_1, \ \hat{\phi}_2, \ \text{and } \hat{\phi}_Z^2.$ Also, use the pre-installed function *ar.yw()* for estimation.
  
  
\setlength{\leftskip}{0cm}

