---
title: "Lab Assignment 3"
author: "Dylan Berneman"
date: '2023-04-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Question 1
Consider the AR(2) process below:
$$
\begin{aligned}
X_t = 0.8\ X_{t-1}\ - 0.12\ X_{t-2}\ + Z_{t}\ \text{with }Z_{t}  \stackrel{iid}{\sim} N(0, 1)
\end{aligned}
$$
\setlength{\leftskip}{2cm}

  (a) Express the process in terms of the back shift operator, *B*.  
  
  $$Z_{t}=(1-0.8\ B+0.12\ B^2)X_{t}$$
  \
  
  (b) Determine whether each process is causal and/or invertible. (Hint: use *polyroot()*)\
```{r}
polyroot(c(1,-0.8,0.12))
```
  Since the roots are outside of the unit circle, the AR(2) model is causal.\
  \

  (c) Plot the sample ACF and PACF after simulating 200 observations from this AR(2) model with the following code:  
```{r}
set.seed(1234)

ar2 <- arima.sim(model = list(ar = c(0.8, -0.12), sd = 1), n = 200)
acf(ar2)
pacf(ar2)
```  
  \

  (d) Use the above simulation to **manually** construct the Yule-Walker estimate $\hat{\phi}_1, \ \hat{\phi}_2, \ \text{and } \hat{\phi}_Z^2.$ Also, use the pre-installed function *ar.yw()* for estimation.
```{r}
acv_ar <- acf(ar2,type = "covariance",main = "Sample ACF",plot = F)
Rho <- toeplitz(acv_ar$acf[c(1,2)]/acv_ar$acf[1])
rho <- acv_ar$acf[c(2,3)]/acv_ar$acf[1]
phi_hat <- solve(Rho) %*% rho 
phi_hat
sigma_z <- acv_ar$acf[1]*(1-t(rho)%*%solve(Rho)%*%rho) 
sigma_z
yw <- ar.yw(ar2,order = 2) 
yw$x.mean
yw$ar
yw$var.pred
```  
