---
title: "Lab 6 Assignment"
author: "Dylan Berneman"
output: html_document
date: '2023-05-13'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(astsa)
```

### Question 1

(a) Summarize how you would carry out the following steps in time series analysis. You can describe briefly by words, or write down R commands you would use to implement these steps.\

  • Step 1 Data processing (make the data stationary)
```{r}
covid <- read.csv("owid-covid-data 2.csv")

covid[(is.na(covid))]<-0

covid <- covid %>%
  group_by(date) %>%
  summarise(across(c(total_cases, new_cases, new_cases_smoothed, total_deaths, new_deaths, new_deaths_smoothed), sum))

covid["Smoothed_New_Case_Fatality_Rate"] = NA

for(i in 1:1225){
  covid$Smoothed_New_Case_Fatality_Rate[i] = covid$new_deaths_smoothed[i] / covid$new_cases_smoothed[i]}

covid <- covid[346:1225,]

Mortality = ts(covid$Smoothed_New_Case_Fatality_Rate)

# check for seasonality
frequency(Mortality)

# plot w/ mean line
plot.ts(Mortality)
abline(reg=lm(Mortality~time(Mortality)), col="red")

# plot acf
Mortality_acf1 = acf2(Mortality)

# get variance
var(Mortality)

# variance is stable
# just to check for transformations

# square root transform
Mortality.Sqrt = sqrt(Mortality)
# variance is much greater than the original series
var(Mortality.Sqrt)

# log transform
Mortality.log = log(Mortality)
# variance is much greater than the original series
var(Mortality.log)

# try differencing
Mortality.diff = diff(Mortality, 1)

# stop once mean is a horizontal line
plot.ts(Mortality.diff)
abline(reg=lm(Mortality.diff~time(Mortality.diff)), col="red")

# smaller variance than the original
var(Mortality.diff)

Mortality.diff2 = diff(Mortality, 2)
plot.ts(Mortality.diff2)
abline(reg=lm(Mortality.diff2~time(Mortality.diff2)), col="red")
# larger variance than 1st difference
var(Mortality.diff2)

# Diff = 1
var(Mortality.diff) < var(Mortality.diff2)

# Match ACF to theoretical
Mortality.diff_acf1 = acf2(Mortality.diff)
``` 
\
Then match theoretical p/acf to sample p/acf to find p and q\

  • Step 2 Model identification\
      - Find a theoretical stationary model that has similar acf/pacf to the sample\
      
  • Step 3 Model estimation\
    - Use arima, yw, innovation algorithm, and mle to estimate the model coefficients\
    
  • Step 4 Model selection\
    - Use AICc to find the model with the lowest value.\
    
  • Step 5 Model diagnostics\
    - Examine normal Q-Q plot
    - Ran Shapiro-Wilk test of normality
    -check sample acf/pacf of residuals resembles WN 95% ci
    - Portmanteau tests\
    
  • Step 6 Data forecast\
    - Forecast future observations\
\    
    
  (b) Review this week’s lab material, Dow Jones Index question part 3) (‘Make the data stationary’). Is  differencing once at lag 1 sufficient to make the data stationary? If yes, justify it. If no, try to make it stationary. Please write related R Codes.
  
```{r}
dowj_data <- scan("dowj.txt")
dowj <- ts(dowj_data)
ts.plot(dowj,main = "Dow Jones Index")
acf = acf2(dowj)
dowj.diff = diff(dowj, 1)
ts.plot(dowj.diff,main = "Dow Jones Index")
abline(reg=lm(dowj.diff~time(dowj.diff)), col="red")
acf2 = acf2(dowj.diff)
```
\
Differencing once at lag 1 is enough to make the time series stationary. As can be seen in the acf and pacf of the differenced time series, a majority of the values at each lag are within the confidence interval.