---
title: 'Lab Assignment #5'
author: "Dylan Berneman"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 1
We will analyze monthly milk production measured in pounds per from Jan. 1962 to Dec. 1975 from the package tsdl as Lab 4 (if you want to re-install tsdl, please refer to Lab 4). Let’s denote the time series milk as X~t~.

```{r}
library(tsdl)
milk <- subset(tsdl, 12, "Agriculture")[[3]] plot(milk)
```
\
```{r}
# To make it more stationary, we use the following code:
dmilk <- diff(milk, 12) ddmilk <- diff(dmilk, 1)
```
\
(a) Explain why the series milk looks not stationary.\


(b) Let Y~t~ be the series ddmilk, that is, Y~t~ = (1 − B)(1 − B~12~)X~t~. Plot the ACF and PACF of Y~t~ with lag.max = 50.\

\
(c) Now, we assume that Y~t~ corresponds to a SARIMA model. Determine possible candidate
models SARIMA(p, d, q) × (P, D, Q)s for the series Y~t~.\

\
(d) Choose one model for this data set, and write down your fitted model.\
