---
title: 'Lab Assignment #5'
author: "Dylan Berneman"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(FinTS)
library(latex2exp)
library(astsa)
library(polynom)
```

### Question 1
We will analyze monthly milk production measured in pounds per from Jan. 1962 to Dec. 1975 from the package tsdl as Lab 4 (if you want to re-install tsdl, please refer to Lab 4). Let’s denote the time series milk as X~t~.

```{r}
#devtools::install_github("FinYang/tsdl") # install the `tsdl` package from github
library(tsdl)
milk <- subset(tsdl, 12, "Agriculture")[[3]] 
plot(milk)
```
\
```{r}
# To make it more stationary, we use the following code:
dmilk <- diff(milk, 12) 
ddmilk <- diff(dmilk, 1)
plot(ddmilk)
```
\
(a) Explain why the series milk looks not stationary.\

`milk` looks stationary because it looks like it has a positive trend as well as seasonality.

(b) Let Y~t~ be the series ddmilk, that is, Y~t~ = (1 − B)(1 − B~12~)X~t~. Plot the ACF and PACF of Y~t~ with lag.max = 50.\
```{r}
acf(ddmilk, lag.max=50)
pacf(ddmilk, lag.max=50)
```

\
(c) Now, we assume that Y~t~ corresponds to a SARIMA model. Determine possible candidate
models SARIMA(p, d, q) × (P, D, Q)s for the series Y~t~.\

SARIMA(0,1,0) x (0,1,0)~12~


\
(d) Choose one model for this data set, and write down your fitted model.\

```{r}
x = sarima(milk, 0,1,0,0,1,0,12)
plot(x$fit$residuals)
```
