---
title: "PSTAT 174/274, Spring 2023: Homework #3"
author: "Dylan Berneman"
date: '2023-04-22'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Note: {Z~t~} ∼ WN(0, σ~Z~^2^ ) denotes white noise.*\
\

### Question 1

You are given the following time series model: $X_t = \frac23 X_{t−1} + \frac12 X_{t−2} + Z_t$. Determine whether this time series is stationary and/or invertible.

```{r}
polyroot(c(1, -2/3, -1/2))
```
The time series is invertible because all AR models are invertible. It has a root within the unit circle, so it cannot be stationary.
\
\

### Question 2
You are given the following statements about a time series modeled as an AR(3) process:\

(I)    Partial Autocorrelation for lag 3 is always equal to zero.   
(II) Partial Autocorrelation for lag 4 is always equal to zero.    
(III) Partial Autocorrelation for lag 4 is always greater than zero.\

Determine which of the above statements are true.\

(I)  False. The PACF for an AR(p) model at lag p cannot be equal to 0.
(II)  True. The partial autocorrelation at lag k of an AR(p) time series is 0 at all lags k>p. Since p=3 and k=4, PACF $\phi_{4}=0$
(III)  False. The partial autocorrelation at lag k of an AR(p) time series is 0 at all lags k>p.
\
\

### Question 3
For a stationary ARMA(1,1) model, you are given the following information: ρ~X~(1) = 0.7, ρ~X~(2) = 0.3. Calculate $\phi_{1}$.

*Hint: Formulas for ACF of ARMA (1,1) model X~t~ − $\phi_1$X~t−1~ = Z~t~ + θ~1~ Z~t−1~ are given in §5.1 of lecture notes and slide 24 of week 3.  \
Can you determine a recursive relation between ρ~X~(k) and ρ~X~ (k−1)? Use it!*
\
\

### Question 4 
You are given PACF for a stationary process: $\phi_{11}$ = −0.60, $\phi_{22}$ = 0.36, $\phi_{kk}$ = 0 for k ≥ 3. What time series model could have this PACF?  
Identify model’s coefficients and write model equation.\

*Hint: • §6 of Lecture Notes and slides 32-33 of Week 3 provide relationship between PACF and ACF, allowing to calculate ACFs of the model from given PACFs.  
• Yule-Walker equations, in §4.3 of Lecture Notes and on slide 14, Week 3, provide relationship between ACF and model coefficients.*
\
\

### Question 5
You are given the following time-series model: X~t~ = 0.8X~t−1~ + 2 + Z~t~ − 0.5Z~t−1~.   
Which of the following statements about this model is false?\

(A) ρ~X~(1) = 0.4.\

(B) ρ~X~(k) < ρX(1),k ≥ 2.\

(C) The model is ARMA(1,1).\

(D) The model is stationary.\

(E) The mean, μ~X~, is 2.
\
\

### Question 6
The Notion of parameter redundancy pertains to the situation when AR and MA characteristic polynomials $\phi$(z) and θ(z) share a common factor, in which case the model may be simplified.
Determine which of the following models are parameter redundant:

(I)    X~t~ = $\frac12$ X~t−1~ +Z~t~ − $\frac12$ Z~t−1~;

(II)  X~t~ = $\frac12$ X~t−1~ +Z~t~ − $\frac19$ Z~t−2~; 

(III) X~t~ = $-\frac56$X~t−1~ − $\frac16$X~t−2~+Z~t~ + $\frac{8}{12}$Z~t−1~ + $\frac{1}{12}$Z~t−2~.
\
\

**The following problems are for students enrolled in PSTAT 274 ONLY**
\

### Question GE 1
Show that the two MA(1) processes  X~t~ = Z~t~ + θ Z~t−1~,  {Z~t~}∼WN(0, σ^2^), and Y~t~ = Z̃~t~ + $\frac1θ$Z̃~t−1~,  {Z̃~t~} ∼ WN(0, σ^2^θ^2^), where 0 < |θ| < 1, have the same autocovariance functions.
\
\

### Question GE 2
You are given the following time series model: X~t~ = $\phi$X~t−1~ + Z~t~. Let Y~t~ = X~2t~, that is, the original process observed only at even times. Show that Y~t~ is also an AR(1) model Y~t~ = $\phi$~∗~Y~t−1~ + Z~t~^∗^ and determine $\phi$^∗^ and Z~t~^∗^, that is, express $\phi$^∗^ and Z~t~^∗^ via $\phi$ and Z~t~
