---
title: "PSTAT 174/274, Spring 2023: Homework #3"
author: "Dylan Berneman"
date: '2023-04-22'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Note: {Z~t~} ∼ WN(0, σ~Z~^2^ ) denotes white noise.*\
\

### Question 1

You are given the following time series model: $X_t = \frac23 X_{t−1} + \frac12 X_{t−2} + Z_t$. Determine whether this time series is stationary and/or invertible.

```{r}
polyroot(c(1, -2/3, -1/2))
```
The time series is invertible because all AR models are invertible. It has a root within the unit circle, so it cannot be stationary.
\
\

### Question 2
You are given the following statements about a time series modeled as an AR(3) process:\

(I)    Partial Autocorrelation for lag 3 is always equal to zero.   
(II) Partial Autocorrelation for lag 4 is always equal to zero.    
(III) Partial Autocorrelation for lag 4 is always greater than zero.\

Determine which of the above statements are true.\

(I)  False. The PACF for an AR(p) model at lag p cannot be equal to 0.
(II)  True. The partial autocorrelation at lag k of an AR(p) time series is 0 at all lags k>p. Since p=3 and k=4, PACF $\phi_{4}=0$
(III)  False. The partial autocorrelation at lag k of an AR(p) time series is 0 at all lags k>p.
\
\

### Question 3
For a stationary ARMA(1,1) model, you are given the following information: ρ~X~(1) = 0.7, ρ~X~(2) = 0.3. Calculate $\phi_{1}$.

*Hint: Formulas for ACF of ARMA (1,1) model X~t~ − $\phi_1$X~t−1~ = Z~t~ + θ~1~ Z~t−1~ are given in §5.1 of lecture notes and slide 24 of week 3.  \
Can you determine a recursive relation between ρ~X~(k) and ρ~X~ (k−1)? Use it!*
$$
\begin{aligned}
\text{For ARMA(1,1): }&\ \rho_X(k) = \frac{(\phi_1+\theta_1)(1+\phi_1\theta_1)}{1+2\phi_1\theta_1+\theta_1^2}\ \phi_1^{k-1} = Constant\  *\ \phi_1^{k-1}, \ k>0\\ 
&\text{that is, } \rho_X(k+1)=\Phi_1\rho_X(k)\ \text{or } \rho_X(2)= \Phi_1\rho_X(1),\ \Phi_1=\rho_X(2)/\rho_X(1)\\\\
&\text{Given: }\\ 
&\rho_X(1)= 0.7\ \ \ \ \&\ \ \ \ \rho_X(2)=0.3,\\
&\phi_1 = 3/7
\end{aligned}
$$
\
\

### Question 4 
You are given PACF for a stationary process: $\phi_{11}$ = −0.60, $\phi_{22}$ = 0.36, $\phi_{kk}$ = 0 for k ≥ 3. What time series model could have this PACF?  
Identify model’s coefficients and write model equation.\

*Hint: • §6 of Lecture Notes and slides 32-33 of Week 3 provide relationship between PACF and ACF, allowing to calculate ACFs of the model from given PACFs.  
• Yule-Walker equations, in §4.3 of Lecture Notes and on slide 14, Week 3, provide relationship between ACF and model coefficients.*\

AR(2): X~t~ = 0.6X~t-1~ - 0.36X~t-2~ + Z~t~
$$
\begin{aligned}
\alpha(1):\ & \phi_{11} = \rho_X(1)=-0.60\\
\alpha(2): \ & \phi_{22} = \frac{\rho_X(2)-(\rho_X(1))^2}{1-(\rho_X(1))^2} \\
&0.36= \frac{\rho_X(2)-(-0.60)^2}{1-(-0.60)^2}\\
& \ \ \ \ \ \ \ \ = \frac{\rho_X(2)-0.36}{1-0.36}\\
&\rho_X(2) = (0.36)(0.64)+0.36 \\
& \ \ \ \ \ \ \ \ \ \ = 0.5904\\\\
\end{aligned}
$$
$$
\begin{aligned}
ACF\rightarrow\ & \rho_X(1)=\phi_1+\phi_2\rho_X(1)\\
& \rho_X(1)=\frac{\phi_1}{1-\phi_2} \\
& -0.60 = \phi_1+\phi_2(-0.60)\\
& -0.60 = \frac{\phi_1}{1-\phi_2}\\\\
&\phi_1+\phi_2(-0.60) = \frac{\phi_1}{1-\phi_2}\\
&\phi_1-0.60\phi_2-\phi_1\phi_2+0.60\phi_2^2=\phi_1\\
&-0.60\phi_2+0.60\phi_2^2=\phi_1\phi_2\\
&-0.60\phi_2(1-\phi_2)=\phi_1\phi_2\\
&-0.60(1-\phi_2)=\phi_1\\
***\phi_1***\ \ \ \ \ \ \ \ \ \ & \phi_1 = 0.60\phi_2 - 0.60
\end{aligned}
$$
$$
\begin{aligned}
ACF\rightarrow\ & \rho_X(2)=\phi_1\rho_X(1)+\phi_2\\
& \rho_X(2)=\frac{\phi_1^2+\phi_2(1-\phi_2)}{1-\phi_2}\\
& 0.5904=\phi_1(-0.60) + \phi_2\\
& 0.5904= \frac{\phi_1^2+\phi_2(1-\phi_2)}{1-\phi_2}\\\\
\phi_1(-0.60) + \phi_2 & = \frac{\phi_1^2+\phi_2(1-\phi_2)}{1-\phi_2}\\\\
-0.60\phi_1+\phi_2+0.60&\phi_1\phi_2-\phi_2^2 = \phi_1^2+\phi_2(1-\phi_2)\\
-0.60\phi_1+\phi_2+0.60&\phi_1\phi_2-\phi_2^2 = \phi_1^2+\phi_2-\phi_2^2\\
-0.60\phi_1+0.60&\phi_1\phi_2 = \phi_1^2\\
0.60\phi_2-&0.60=\phi_1\\
0.60\phi_2&=\phi_1+0.60\\
\phi_2&=1 + \frac{\phi_1}{0.60}\\
***\phi_1***\ \ \ \ \ \ \ \ \ \ \phi_2&=1+\frac53\phi_1
\end{aligned}
$$

$$
\begin{aligned}
&\phi_1 = 0.60\phi_2 - 0.60\\
&\phi_2=1+\frac53\phi_1\\\\

& 0.5904=\phi_1(-0.60) + \phi_2\\
& 0.5904=-0.60(0.60\phi_2-0.60)+\phi_2\\
& 0.5904-0.36=0.64\phi_2\\
& 0.2304 = 0.64\phi_2\\
&\phi_2=0.36\\\\

&\phi_1 = 0.60\phi_2 - 0.60\\
&\phi_1 = 0.60(0.36) - 0.60\\
&\phi_1 = 0.216-0.60\\
&\phi_1=-0.384\\
\end{aligned}
$$
AR(2) Model: $X_t = -0.384\ X_{t-1} + 0.36\ X_{t-2} + Z_t$
\
\

### Question 5
You are given the following time-series model: X~t~ = 0.8X~t−1~ + 2 + Z~t~ − 0.5Z~t−1~.   
Which of the following statements about this model is false?\

(A) ρ~X~(1) = 0.4.\
True.
$$
\begin{aligned}
\rho_X(k)&=\frac{(\phi_1+\theta_1)(1+\phi_1\theta_1)}{1+2\phi_1\theta_1+\theta_1^2}\ \phi_1^{k-1}\\
\rho_X(1)&=\frac{(0.8-0.5)(1+(0.8)(-0.5))}{1+2(0.8)(-0.5)+(-0.5)^2}\ (0.8)^{1-1}\\
&= \frac{0.3(0.6)}{1-0.8+0.25}\\
&=0.4\\
\end{aligned}
$$
\

(B) ρ~X~(k) < ρX(1),k ≥ 2.\
True.
$$
\begin{aligned}
\rho_X(k)&=\rho_X(1) * \phi_1^{k-1}\\
\text{Since } &\phi_1 <1,\ \phi_1^x < 1\ \text{for } x\geq2
\end{aligned}
$$\

(C) The model is ARMA(1,1).\
True. It is of the form X~t~ - $\phi_1$X~t-1~ = Z~t~ - $\theta_1$Z~t-1~\ 

(D) The model is stationary.\
True. $|\theta_1|<1\ \ \&\ \ |\phi_1| < 1$ and the roots are outside of the unit circle.

(E) The mean, μ~X~, is 2.\
False. 
$$ 
\begin{aligned}
E[X_t] &= E[0.8X_{t-1} +2]\\
µ_X& = 0.8µ_X + 2\\
0.2µ_X &=2\\
µ_X &= 10
\end{aligned}
$$
\
\

### Question 6
The Notion of parameter redundancy pertains to the situation when AR and MA characteristic polynomials $\phi$(z) and θ(z) share a common factor, in which case the model may be simplified.
Determine which of the following models are parameter redundant:

(I)    X~t~ = $\frac12$ X~t−1~ +Z~t~ − $\frac12$ Z~t−1~;
$$
X_t = \frac12 X_{t−1} + Z_t − \frac12 Z_{t−1}\\
X_t - \frac12 X_{t−1} = Z_t − \frac12 Z_{t−1}\\
X_t(1-0.5B)=Z_t(1-0.5B)\\
X_t = Z_t\\
\text{Since the model can be simplified, it is redundent.}
$$
(II)  X~t~ = $\frac12$ X~t−1~ +Z~t~ − $\frac19$ Z~t−2~; 
$$
X_t = \frac12 X_{t−1} + Z_t − \frac19 Z_{t−2}\\
X_t - \frac12 X_{t−1} = Z_t − \frac19 Z_{t−2}\\
X_t(1-0.5B)=Z_t(1-\frac19 B^2)\\
\text{Since the model cannot be further simplified, it is not redundent.}
$$
(III) X~t~ = $-\frac56$X~t−1~ − $\frac16$X~t−2~+Z~t~ + $\frac{8}{12}$Z~t−1~ + $\frac{1}{12}$Z~t−2~.
$$
X_t = -\frac56 X_{t−1} -\frac16 X_{t−2}+ Z_t + \frac{8}{12} Z_{t−1} +\frac{1}{12} Z_{t−2}\\

X_t +\frac56 X_{t−1} +\frac16 X_{t−2}= Z_t + \frac{8}{12} Z_{t−1} +\frac{1}{12} Z_{t−2}\\

\frac16 X_t(6+5B+B^2)=\frac{1}{12}Z_t(12+8B+B^2)\\
\frac16 X_t(3+B)=\frac{1}{12}Z_t(6+B)(2+B)\\
\frac12(2+B)\frac13 X_t(3+B)=\frac12(2+B)\frac16Z_t(6+B)\\
\frac13 X_t(3+B)=\frac13\frac12Z_t(6+B)\\
X_t(3+B)=\frac12Z_t(6+B)\\
X_t(3+B)=Z_t(3+\frac12B)\\
\text{Since the model can be simplified, it is redundent.}
$$
\
\

**The following problems are for students enrolled in PSTAT 274 ONLY**
\

### Question GE 1
Show that the two MA(1) processes  X~t~ = Z~t~ + θ Z~t−1~,  {Z~t~}∼WN(0, σ^2^), and Y~t~ = Z̃~t~ + $\frac1θ$Z̃~t−1~,  {Z̃~t~} ∼ WN(0, σ^2^θ^2^), where 0 < |θ| < 1, have the same autocovariance functions.
$$
\begin{aligned}
&Z_t \sim WN(0, \sigma^2) \ \ \ \ \ \ \ \ \ \ \ \tilde{Z_t} \sim WN(0, \sigma^2\theta^2)\\
& Var[Z_t] = \sigma^2\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ Var[\tilde{Z_t}] = \sigma^2\theta^2 \\
& \ \ \ \ \ \ \ \ \ \ \ \ \ = \sigma_X^2\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ = \sigma_X^2 \theta^2 = \sigma_Y^2\\\\

& \text{For }Z_t:\ \theta_1 = \theta \ \ \ \ \ \ \ \ \ \ \ \ \ \text{For }\tilde{Z_t}:\ \theta_1 = \frac1\theta \\
& \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ = \theta_X \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ = \frac{1}{\theta_X} = \theta_Y\\\\

\gamma_{X}(k)&= 
\begin{cases}(1+\theta_{1}^2)\sigma_X^2\ \ \ \ \ \ \ \ for\ \ k = 0\\ \theta_{k}\sigma_X^2 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ for\ \ k=\pm1\\ 0 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ for\ k>1\ or\ k<-1 \end{cases} \\\\

&= \begin{cases}(1+\theta_X^2)\sigma_X^2\ \ \ \ \ \ \ \ for\ \ k = 0\\ \theta_X\sigma_X^2 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ for\ \ k=\pm1\\ 0 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ for\ k>1\ or\ k<-1 \end{cases} \\\\

&= \begin{cases}(1+\theta^2)\sigma^2\ \ \ \ \ \ \ \ for\ \ k = 0\\ \theta\sigma^2 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ for\ \ k=\pm1\\ 0 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ for\ k>1\ or\ k<-1 \end{cases} \\\\\\

\gamma_{Y}(k)&= 
\begin{cases}(1+\theta_{1}^2)\sigma_Y^2\ \ \ \ \ \ \ \ for\ \ k = 0\\ \theta_{k}\sigma_Y^2 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ for\ \ k=\pm1\\ 0 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ for\ k>1\ or\ k<-1 \end{cases} \\\\

&= 
\begin{cases}(1+\frac{1}{\theta_X^2})\sigma_X^2 \theta^2\ \ \ \ for\ \ k = 0\\ \frac{1}{\theta_X}\sigma_X^2 \theta^2 \ \ \ \ \ \ \ \ \ \ \ \ \ for\ \ k=\pm1\\ 0 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ for\ k>1\ or\ k<-1 \end{cases} \\\\

&= 
\begin{cases}(\theta^2+\frac{\theta^2}{\theta^2})\sigma^2 \ \ \ \ \ \ \ \ for\ \ k = 0\\ \frac{\theta^2}{\theta}\sigma^2 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ for\ \ k=\pm1\\ 0 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ for\ k>1\ or\ k<-1 \end{cases} \\\\

&= \begin{cases}(1+\theta^2)\sigma^2\ \ \ \ \ \ \ \ for\ \ k = 0\\ \theta\sigma^2 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ for\ \ k=\pm1\\ 0 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ for\ k>1\ or\ k<-1 \end{cases}\\\\

&Therefore,\ \gamma_{X}(k) = \gamma_{Y}(k)
\end{aligned}
$$
\
\

### Question GE 2
You are given the following time series model: X~t~ = $\phi$X~t−1~ + Z~t~. Let Y~t~ = X~2t~, that is, the original process observed only at even times. Show that Y~t~ is also an AR(1) model Y~t~ = $\phi$~∗~Y~t−1~ + Z~t~^∗^ and determine $\phi$^∗^ and Z~t~^∗^, that is, express $\phi$^∗^ and Z~t~^∗^ via $\phi$ and Z~t~
```{r}
Z=rnorm(100,0,1)
X=Z[1:50]
for(i in 1:50){
  X[i] = Z[2*i-1]
}
i=7
X[i]
Z[2*i-1]
```

$$
\begin{aligned}
X_t &= \phi X_{t−1} + Z_t\\
Y_t &= X_{2t}\\
&= \phi X_{2t−1} + Z_{2t} \\
Y_{t-1} &= X_{2t-1}\\
&= \phi X_{2t−1-1} + Z_{2t-1} \\\\
AR(1)\ model:\ \ Y_t &= \phi^* Y_{t-1} + Z^*_t\\
&= \phi(\phi X_{2t-1-1} +Z_{2t-1}) + Z_{t}\\
& =\phi^2 X_{2t−2} + \phi Z_{2t-1}+Z_t\\
& =\phi^2 Y_{t−1} + \phi Z_{2t-1}+Z_t\\\\
&\phi^* = \phi^2\\
&Z^*_t= \phi Z_{2t-1}+Z_t
\end{aligned}
$$