---
title: "Lab 4 Assignment"
author: "Dylan Berneman"
date: '2023-04-27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Part 1: Data Import
In this question we keep studying Task 1 in Lab 4 where we import monthly-australian-wine-sales-th.csv and use ts() command.

```{r}
wine.csv = read.table("monthly-australian-wine-sales-th.csv",
sep=",", header=FALSE, skip=1, nrows=187)
```

#### Question 1
Compare the plots of the series ‘wine1’ and ‘wine’ defined below, and state why we use ‘frequency=12’ in the lab material.
       wine1 = ts(wine.csv[,2], start = c(1980,1))
       
```{r}
wine1 = ts(wine.csv[,2], start = c(1980,1), frequency = 12)
plot.ts(wine1)
```
      
       wine = ts(wine.csv[,2], start = c(1980,1), frequency = 12)
```{r}
wine = ts(wine.csv[,2], start = c(1980,1))
plot.ts(wine)
```

Both plots are visually identical. The only difference is the x-axis. The time for `wine1` ranges from the years 1980 through the middle of 1995. Meanwhile, the time for `wine` ranges from the years 1980 through 2167. In the data set, `wine.csv`, the time variable is in a date format "YYYY/MM". When creating the time series, the start time is 1980/01. If we use the default of `Frequency`, 1, then that tells the code that each successive observation occurs 1 year later. By changing `Frequency` to 12, the code is told that the each successive observation occurs 1/12 of a year later, which is what we want.
\
\

#### Question 2
If you have a daily data of wine sales, for example from Jan 1, 1981 to Dec 31,1983. What value would you put in ‘frequency=’ so that the plot shows the correct year index on x-axis?\

If we had daily data, we would have to set the frequency to 365, which is the amount of days in a year.
\
\

### Part 2: Data Tranformation
We introduce the Time Series Data Library (TSDL) created by Professor Rob Hyndman.(https://rdrr.io/ github/FinYang/tsdl/f/vignettes/tsdl.Rmd)
Run the following code to import quarterly Iowa nonfarm income in R:

```{r}
#install.packages("devtools") 
install.packages("forecast") 
devtools::install_github("FinYang/tsdl") 
library(tsdl)
library(forecast)
```

```{r}
meta_tsdl$description[[1]]
iowa.ts <- tsdl[[1]]

library(MASS)
t = 1:length(wine1)
fit = lm(wine1 ~ t)
bcTransform = boxcox(wine1 ~ t,plotit = TRUE)

lambda = bcTransform$x[which(bcTransform$y == max(bcTransform$y))] 
wine.bc = (1/lambda)*(wine1^lambda-1)

#log transform
wine.log = log(wine1)
# square root transform
wine.sqrt = sqrt(wine1)
#Compare transforms
op= par(mfrow=c(2,2))
ts.plot(wine1, main = "Original Times Series") 
ts.plot(wine.bc, main = "Box-Cox Transform") 
ts.plot(wine.log, main = "Log Transform") 
ts.plot(wine.sqrt, main = "Square Root Transform")
```