---
title: "PSTAT 174/274, Spring 2023: Homework #4"
output: html_document
date: '2023-05-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(FinTS)
library(latex2exp)
library(astsa)
library(polynom)
```

Note: In all problems, {Z~t~} ∼ WN(0,σ~Z~^2^ ) denotes white noise, and B denotes the backshift operator BX~t~ = X~t−1~.

### Question 1
For each of the models (1)-(3), write corresponding characteristic polynomials θ(z) and $\phi$(z). In other words, write models (1)-(3) as $\phi$(B)X~t~ = θ(B)Z~t~ and specify polynomials θ(z) and $\phi$(z). For each, identify the model as a certain (S)ARIMA model and determine whether the model in invertible and stationary:

(1) X~t~ = −0.2X~t−1~+Z~t~−2Z~t−1~; 
$$
\begin{aligned}
(1+ 0.2 B)X_t &= (1-2B)Z_t\\
\phi(z) &= 1 + 0.2z\\
\theta(z) &= 1-2z\\
&\text{SARIMA}\ (1,0,1) = ARMA(1,1)\\
\text{Because } |\theta| > 1, &\text{the model is not invertible.}\\
\text{Find roots of }\phi (z)&:\ 1-0.2z\ \rightarrow\ \ |z| = 5 > 1\\
&\text{The model is stationary}
\end{aligned}
$$
\
(2) X~t~ = X~t−1~+Z~t~−0.2Z~t−1~−0.7Z~t−2~ 
$$
\begin{aligned}
(1-1B)X_t &= (1-0.2B-0.7B^2)Z_t\\
\phi(z) &= 1 - 1z\\
\theta(z) &= 1-0.2z-0.7z^2\\
&\text{SARIMA}\ (1,0,2) = ARMA(1,2)\\
\text{Because } |\phi| \geq  1,\ &\text{the model is not stationary.}\\
\text{Find roots of }\theta (z)&:\ 1-0.2z-0.7z^2\ \rightarrow\ \ |z| =  (1.060879+0i -1.346593+0i) > 1\\
&\text{The model is invertible.}
\end{aligned}
$$
\

(3) X~t~ = X~t−3~+Z~t~+0.4Z~t−1~−0.45Z~t−2~.
$$
\begin{aligned}
(1-1B^3)X_t &= (1+0.4B-0.45B^2)Z_t\\
\phi(z) &= 1-1z^3\\
\theta(z) &= 1+0.z-0.45z^2\\
&\text{SARIMA}\ (3,0,2) = ARMA(3,2)\\
\text{Because } |\phi| \geq  1,\ &\text{the model is not stationary.}\\
\text{Find roots of }\theta (z)&:\ 1+0.4z-0.45z^2\ \rightarrow\ \ |-1.111111-0i  2.000000+0i| =  z > 1\\
&\text{The model is invertible.}
\end{aligned}
$$
\
### Question 2
Identify the model equation corresponding to SARIMA (0, 0, 2)(0, 0, 1)12 model. 

A. X~t~ = Z~t~ + θ~1~Z~t−1~ + θ~1~2Z~t−2~.
B. X~t~ = Z~t~ + θ~1~Z~t−1~ + θ~2~Z~t−2~ + θ~1~θ~2~Z~t−3~.
C. X~t~ = Z~t~ + θ~1~Z~t−1~ + θ~2~Z~t−2~ + θ~1~θ~2~Z~t−12~.
D. X~t~ = Z~t~ + θ~1~Z~t−2~ + θ~2~Z~t−12~ + θ~1~θ~2~Z~t−14~. 
E. X~t~ = Z~t~ + θ~1~Z~t−1~ + θ~2~Z~t−11~ + θ~1~θ~2~Z~t−12~.
$$
\text{SARIMA (0, 0, 2)(0, 0, 1)}_{12}:\\
X_t = (1+\theta_1B+\theta_2B_2)(1+\Theta_1B^{12})Z_t  \\
X_t=Z_t+\theta_1Z_{t-1} +\theta_2Z_{t-2}+\Theta_1Z_{t-12} + \theta_1\Theta_1Z_{t-13}+\theta_2\Theta_1Z_{t-13}
$$
\
The only option that matches is (D).
\

### Question 3
  (a) For the following SARIMA(p, d, q)×(P, D, Q)~s~ models, specify parameters p, d, q, P, D, Q and s, and write corresponding equations. It is OK to leave equations in the form. $\phi(B)\Phi(B^s) (1−B)^d (1−B^s)^DX_t = θ(B)\Theta(B^s)Z_t$, Z~t~ ∼ WN(0,σ~Z~^2^).\
\
    (i) SARIMA(1, 1, 0) × (1, 1, 2)~6~,  
$$
\begin{cases}
p=1\\ d=1\\ q=0\\ 
\end{cases}
\ \ \ \
\begin{cases} 
P=1\\ D=1\\ Q=2\\ s=6 
\end{cases}\\
(1-\Phi_1B^{12})(1-\theta_1B)(1-B)X_t=(1+\Theta_1B^{12}+\Theta_2B^{24})Z_t
$$
\
    (ii) SARIMA(0, 1, 1) × (0, 0, 3)~12~,
$$
\begin{cases}
p=0\\ d=1\\ q=1\\ 
\end{cases}
\ \ \ \ 
\begin{cases} 
P=0\\ D=0\\ Q=3\\ s=12 
\end{cases}\\
(1-B)X_t=(1+\theta_1B)(1+\Theta_1B^{12}+\Theta_2B^{24}+\Theta_3B^{36})Z_t
$$
\
    (iii) SARIMA(2, 1, 2) × (2, 0, 1)~4~
$$
\begin{cases}
p=2\\ d=1\\ q=2\\ 
\end{cases}
\ \ \ \ 
\begin{cases} 
P=2\\ D=0\\ Q=1\\ s=4
\end{cases}\\
(1-\theta_1B-\theta_2B^2)(1-B)(1-\Phi_1B^4-\Phi_2B^8)X_t=(1+\theta_1B+\theta_2B^2)(1+\Theta_1B^4)Z_t
$$
\
  (b) For the following processes {X~t~}, identify SARIMA (p, d, q) × (P, D, Q)~s~ model:\
    (i) (1 − B^12^)^2X~t~ = (1 − 0.3B)Z~t~  
\
$$SARIMA(0,0,1)×(0,2,0)_{12}$$
\
    (ii) X~t~ = 0.5X~t−6~ + Z~t~ 
\
$$
X_t=0.5X_{t-6}+Z_t\\
(1-0.5B^6)X_t=Z_t\\
SARIMA(0,0,0)×(1,0,0)_6
$$
\
    (iii) (1 − 0.8B)(1 + 0.5B^4^)X~t~ = (1 − 1.5B)Z~t~.
\
$$SARIMA(1,0,1)×(1,0,0)_4$$
\

  (c) You are given a time series model where PACF is zero except for lags 12 and 24. Which model will have this pattern?\

$$
\rho_{12}=\rho_{24}=0\\
SARIMA(0,0,0)×(2,0,0)
$$
\
\

### Question 4
For the processes X~t~ = 0.4X~t−1~ + Z~t~ − 0.7Z~t−1~,\
    (i) Simulate and plot 100 values of the processes\
```{r}
options(scipen = 9)
set.seed(333)
sample <- arima.sim(n=100, list(ar=c(0.4), ma=c(-0.7), sd=1))
plot(sample)
```
\
\
   (ii) Compute and graph their theoretical ACF and PACF using R.\
```{r}
acf_model = ARMAacf(ar = 0.4, ma=c(-0.7), lag.max=10, pacf=FALSE)

pacf_model = ARMAacf(ar = 0.4, ma=c(-0.7), lag.max=10, pacf=TRUE)

par(mfrow=c(1,2))

plotArmaTrueacf(list(ar = 0.4, ma=c(-0.7)), lag.max=10, pacf=FALSE, plot=TRUE,
          xlab="Lag", ylab=c("ACF"),
          ylim=c(-0.25, 0.6), xlim=c(0,10), type="h")

plotArmaTrueacf(list(ar = 0.4, ma=c(-0.7)), lag.max=10, pacf=TRUE, plot=TRUE,
          xlab="Lag", ylab=c("Partial ACF"),
          ylim=c(-0.25, 0.6), xlim=c(1,10), type="h")
title(main=TeX(r'(Theoretical ARMA(1,1): $\phi_1$ = 0.4, $\theta_1$ = -0.7)'), line=-1, outer=TRUE, cex=0.5)
```
\
\
    (iii) Compute and graph their sample ACF and PACF using R. How do sample functions compare to their theoretical counterparts?\
```{r}
acf2(sample, max.lag = 10, xlim=c(0,10), ylim=c(-0.25,0.6))
acf2(sample, max.lag = 10, xlim=c(0,10), ylim=c(-0.25,0.6), plot=FALSE)
```
There are not enough sample observations for the sample pacf and acf to be a good estimation of the theoretical pacf and acf.
\
\
    (iv) Analyze smoothness of the simulated processes using their ACF’s.
Please include the code with clear comments explaining the meaning of the code. Make sure to label the graphs.\
```{r}
# Unaltered ACF
plot(sample, ylab = TeX(r'($X_t$)'), xlab="Time")
title(main=TeX(r'(Sample ARMA(1,1): $\phi$ = 0.4, $\theta$ = -0.7)'), line=-1, outer=TRUE, cex=0.5)

# Smoothing by changing ma = -0.7 to ma = 0.7 
sample2 <- arima.sim(n=100, list(ar=c(0.4), ma=c(0.7), sd=1))
plot(sample2, ylab = TeX(r'($X_t$)'), xlab="Time")
title(main=TeX(r'(Sample ARMA(1,1): $\phi$ = 0.4, $\theta$ = 0.7)'), line=-1, outer=TRUE, cex=0.5)
```

\
\
**The following problems are for students enrolled in PSTAT 274 ONLY**
\

### Question GE1
Let {Y~t~} be the AR(1) plus noise time series defined by Y~t~ = X~t~ +W~t~, where {W~t~} ∼ WN(0, σ~W~^2^), {X~t~} is the AR(1) process X~t~ − $\phi$ X~t−1~ = Z~t~,\
{Z~t~} ∼ WN(0, σ~Z~^2^), |$\phi$|<1, and E(W~s~Z~t~) = 0 for all t, s.\

  (a) Show that {Y~t~} is stationary and find its autocovariance function.
\
$$
\begin{aligned}
\text{Given:} &\\
&\begin{cases}
X_t=\phi_1X_{t-1}+Z_t\\
|\phi_1|<1\\
Z_t=WN(0,\ \sigma_Z^2)\\
Y_t=X_t+W_t\\
W_t=WN(0,\ \sigma_W^2)\\
E[W_sZ_t]=0\\
\end{cases}\\\\
X_t\ &\text{is a stationary AR(1) process}\\
&\text{because } \phi(z) = 1-\phi_1z = 0\\
&\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 1=\phi_1z\\
&\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 1/\phi_1 = z\\
&\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \text{if } \phi_1<1,\ \text{then } 1/\phi_1 >1,\\
&\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \text{thus }z>1\\
\end{aligned}
$$
\
$$
\begin{aligned}
Var[X_t] &= \gamma_X(0)= \frac{\sigma_Z^2}{1-\phi_1^2}\\\\
E[Y_t]&=E[X_t+W_t]\\
&= E[X_t]+E[W_t] = 0 \\\\
Var[Y_t] &= Var[X_t+W_t]\\
&= E[(\phi_1X_{t-1}+Z_t+W_t)X_{t-k}]\\
&=E[\phi_1X_{t-1}X_{t-k}]\ +\  E[Z_tX_{t-k}]\ +\ E[W_tX_{t-k}]\\\\
&for\ \ k=0: \ \ \ \
\begin{cases}
E[\phi_1X_{t-1}X_{t}] \ \ \ \ \ \ \ \ \ \ =  \phi_1\gamma_X(1) \\
E[Z_tX_{t}] = E[Z_t^2] \ \ \ = \sigma_Z^2\\
E[W_tX_{t}] = E[W_t^2] \ = \sigma_W^2
\end{cases}\\\\
& Var[Y_t]=\gamma_Y(0) =\phi_1^2\gamma_X(0)+\sigma_Z^2+\sigma_W^2\\\\
\end{aligned}
$$
\
E[\phi_1X_{t-1}X_{t-k}]\ +\ E[\phi_1X_{t-1}W_{t-k}]\ + \\
& \ \ \ \ \ E[Z_tX_{t-k}]\ +\ E[Z_tW_{t-k}]\ + \ E[W_tX_{t-k}]\ + \\ 
& \ \ \ \ \ E[W_tW_{t-k}]
$$
\begin{aligned}
\text{If}\ \ &\phi_1^2\gamma_X(0) +\sigma_Z^2 =\frac{\phi_1^2\sigma_Z^2}{1-\phi_1^2} + \frac{\sigma_Z^2(1-\phi_1^2)}{1-\phi_1^2}= \frac{\sigma_Z^2}{1-\phi_1^2}, \\\\
\text{then}\ \ &\phi_1^2\gamma_X(0) +\sigma_Z^2+\sigma_W^2 =\frac{\phi_1^2(\sigma_Z^2+\sigma_W^2)}{1-\phi_1^2} + \frac{(\sigma_Z^2+\sigma_W^2)(1-\phi_1^2)}{1-\phi_1^2}= \frac{\sigma_Z^2+\sigma_W^2}{1-\phi_1^2} \\\\
&\gamma_Y(k)=\begin{cases}\frac{\sigma_Z^2+\sigma_W^2}{1-\phi_1^2} \ \ \ \ \ \ \ \ \ \ \ \ \text{for k=0}\\\\  \frac{\phi_1^k(\sigma_Z^2+\sigma_W^2)}{1-\phi_1^2}\ \ \ \ \ \ \ \text{for k}\geq1
\end{cases}\ 
\end{aligned}
$$
\  
  (b) Show that the time series U~t~ := Y~t~ − $\phi Y_{t−1}$ is 1-correlated (i.e., γ~U~(h) = 0 for h > 1) and hence is MA(1) process.\
$$
\begin{aligned}
U_t&=Y_t - \phi Y_{t-1}\\
&= X_t+W_t-\phi (X_{t-1}+W_{t-1})\\
&= X_t-\phi X_{t-1}+W_t-\phi W_{t-1}\\
&=(1-\phi B)(X_t+W_t)\\
\text{This is a MA(1) process with }& Z_t \text{ substituted for } X_t+W_t\\
& \&\ X_t  \text{ substituted for }Y_t
\end{aligned}
$$
\  
  (c) Conclude from (b) that {Y~t~} is an ARMA(1,1) process and express the three parameters of this model in terms of $\phi$, σ~W~^2^ and σ~Z~^2^.
\  
$$
U_t =(1-\phi B)(X_t+W_t)\\
Y_t - \phi Y_{t-1} = (1-\phi B)(X_t+W_t)\\
(1-\phi B)(Y_t) = (1-\phi B)(X_t+W_t)\\
\text{Thus, it is an ARMA(1,1) Process}
$$
\
\

### Question GE2 
Find the ACVF, ACF and PACF for {X~t~} when X~t~ = ΦX~t−4~ + Z~t~, |Φ| < 1.\

$$
X_t-\Phi X_{t-4}=Z_t\\
= (1-\Phi B^{1*4})X_{t} = Z_t\\
SARIMA(0,0,0) × (1,0,0)_4 
$$
```{r}
ARMAacf(order=c(0,0,0), seasonal=list(c(1,0,0), period=4))
```
